---
title: "Weight of Fish"
author: "Maria Cabanillas"
date: "12/04/2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```


```{r}
Fishdata=read.csv("Fish.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We are using numerical~numerical because the variables we are looking at are all numerical explantory variables

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
FishiesP=filter(Fishdata, Species == "Perch")
Fishies = select(FishiesP,-Species)
pairs(Fishies)
```

```{r}
FishiesB=filter(Fishdata, Species == "Bream")
Fishies = select(FishiesB,-Species)
pairs(Fishies)
```

```{r}
FishiesS=filter(Fishdata, Species == "Smelt")
Fishies = select(FishiesS,-Species)
pairs(Fishies)
```

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->



### Numerical Descriptive Results

```{r}
summary(FishiesP)
summary(FishiesB)
summary(FishiesS)
```


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
Perchmodel=lm(Weight~Length2+Width,data=Fishies)
summary(Perchmodel)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Fishies,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


```{r}
Breammodel=lm(Weight~Length2+Width,data=Fishies)
summary(Breammodel)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Fishies,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
Smeltmodel=lm(Weight~Length2+Width,data=Fishies)
summary(Smeltmodel)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Fishies,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$ The null hypothesis is that there would be no difference in the way the fishies were measured.
$H_A$ The alternative hypothesis determined that there is a difference in the way the fishies weight was determined.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We used three models to predict the weight of these fish for the Perch the best explanatory variables were height and width.

We used three models to predict the weight of these fish for the Bream the best explanatory variables were length1,height and width.

We used three models to predict the weight of these fish for the Smelt the best explanatory variables were length1, length2, height and width.
